Improving content discovery through combining linked data and data mining techniques

### 2015-12-21 report/report.tex
Building up maxmimal pipeline

        IRI -> RDFa [label="dereference"];
        RDFa -> RDF [label="parse"];
        RDF -> RDF1 [label="derefence/parse"];
        RDF -> RDF2 [label="dereference/parse"];
        RDF -> RDFp [label="\cup"];
        RDF1 -> RDFp [label="\cup"];
        RDF2 -> RDFp [label="\cup"];
        RDFp -> Features [label="content\_?p\_?v"];
      }
    \end{dot2tex}
  \end{center}
  \caption{\label{fig:object.-deref}Semantic web content miner with addtional dereferencing of linked entities}
\end{sidewaysfigure}

@@

        IRI -> RDFa [label="parse"];
        IRI -> Entities [label="extract"];
        IRI -> Linked [label="scrape"];

        RDFa -> RDF [label="\cup"];
        Entities -> RDF [label="\cup"];
        Linked -> RDF [label="\cup"];

>>>>

        IRI -> RDFa [label="dereference"];
        RDFa -> RDF [label="parse"];
        RDF -> RDF1 [label="dereference/parse"];
        RDF -> RDF2 [label="dereference/parse"];
        RDF -> RDFp [label="\cup"];
        RDF1 -> RDFp [label="\cup"];
        RDF2 -> RDFp [label="\cup"];
        RDFp -> Features [label="content\_?p\_?v"];
      }
    \end{dot2tex}
  \end{center}
  \caption{\label{fig:object.-deref}Semantic web content miner with addtional dereferencing of linked entities}
\end{sidewaysfigure}

@@

        node [shape=circle,margin="0,0"]
        RDF1 [label="RDF_1"];
        RDF2 [label="RDF_2"];
        RDF3 [label="RDF_3"];
        RDFp [label="RDF'"];
        RDFp1 [label="RDF'_1"];
        RDFp2 [label="RDF'_2"];
        RDFp3 [label="RDF'_3"];
        RDFp4 [label="RDF'_4"];

        IRI -> RDF1 [label="parse"];
        IRI -> RDF2 [label="extract"];
        IRI -> RDF3 [label="scrape"];

        RDF1 -> RDF [label="\cup"];
        RDF2 -> RDF [label="\cup"];
        RDF3 -> RDF [label="\cup"];

        RDF -> RDFp1 [label="dereference/parse"];
        RDF -> RDFp2 [label="hypernym inference"];
        RDF -> RDFp3 [label="expert inference"];
        RDF -> RDFp4 [label="OWL inference"];

        RDF -> RDFp [label="\cup"];
        RDFp1 -> RDFp [label="\cup"];
        RDFp2 -> RDFp [label="\cup"];
        RDFp3 -> RDFp [label="\cup"];
        RDFp4 -> RDFp [label="\cup"];
